---
title: "p8105_hw5_fl2569"
author: "Fang Liu"
date: "11/16/2021"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)

#figure size options
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

#set theme settings
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1  

First, clean the data. 
```{r, message = FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Focus on Baltimore, MD. The proportion of unsolved homicides is unsolved homicides / total # of homicides.
```{r, message=FALSE}
prop.test(x = 5, n = 10)

baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD") #2827 total homicides

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),#1825 unsolved homicides
    n = n()
)

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
  ) #64% of the homicides in Baltimore is unsolved... 

baltimore_test %>% 
  broom::tidy()
```

Let's try iterate across all the cities! :) 

First, write a function. 
```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),#1825 unsolved homicides
      n = n()
    )

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  #64% of the homicides in Baltimore is unsolved... 

  return(city_test) #city_test is a list of the prop.test results
}
```

Let's test the function we just wrote. 
```{r, message = FALSE}
prop_test_function(baltimore_df)

prop_test_function(
  homicide_df %>% 
    filter(city_state == "AlbuquerqueNM")
)

#OR
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across ALL cities. 
```{r}
nested_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>%  #create nested listed
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  )

#test
nested_df %>% 
  filter(city_state == "BaltimoreMD") %>% 
  pull(tidy_results)
```

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>%  #create nested listed
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf")) %>% 
  arrange(estimate) #order from least unsolved homicide to highest unsolved homicide
```

Try make a plot showing estimates and confidence intervals.
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Another way of solving the problem using `map2`:  
```{r, message = FALSE}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2  

* Start with a data frame containing all file names (the `list.files` function will help)
* Iterate over file names and read in data for each subject using `purrr::map` and saving the result as a new variable in the data frame
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
* Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups  
```{r, message = FALSE}
complete_data =
  tibble(
    files = list.files("./data/zip_data")
  ) %>% 
  mutate(
    data = map(str_c("./data/zip_data/", files), read_csv)
  ) %>% 
  unnest(data) %>%
  mutate(
    arm = substr(files,1, 3),
    subject_id = substr(files, 1, 6)
  ) %>% 
  select(arm, subject_id, everything(), -files) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  )

complete_data %>% 
  ggplot(aes(x = week, y = value, group = subject_id, colour = arm)) +
  geom_line(size = 1) + 
  ggtitle("Change in value for control and experimental arm across time")
```
Participants in the experimental arm seems to be improving (assuming that a higher value implies better patient outcome), while those in the control arms didn't improve or even showed signs of deterioration. 


## Problem 3

There are two cases to address:
* For numeric variables, you should fill in missing values with the **mean** of non-missing values.
* For character variables, you should fill in missing values with **virginica**.

First, load the iris data set from the tidyverse package and introduces some missing values in each column.
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function that takes a vector as an argument, replaces missing values using the rules above, and returns the resulting vector. 
```{r}
fill_in_missing = function(input_vector){
  if (is.numeric(input_vector)) {
    input_vector[is.na(input_vector)] <- round(
      mean(input_vector, na.rm = TRUE),1)
  } else if (is.character(input_vector)) {
    input_vector[is.na(input_vector)] <- "virginica"
  }
  
  return(input_vector)
}
```

Apply this function to the columns of iris_with_missing using a map statement.
```{r}
iris_filled = as.data.frame(map(iris_with_missing, fill_in_missing))
iris_filled
```
